Divergent Impacts of COVID-19 School Closures on Youth Infection Dynamics: Evidence from 12 European Countries

### 2025-06-05 manuscript_njd/manuscript.tex
update + njd

% interactcadsample.tex
% v1.04 - May 2023

\documentclass[]{interact}

\usepackage{epstopdf}% To incorporate .eps illustrations using PDFLaTeX, etc.
\usepackage{subfigure}% Support for small, `sub' figures and tables
%\usepackage[nolists,tablesfirst]{endfloat}% To `separate' figures and tables from text if required

\usepackage{natbib}% Citation support using natbib.sty
\bibpunct[, ]{(}{)}{;}{a}{}{,}% Citation support using natbib.sty
\renewcommand\bibfont{\fontsize{10}{12}\selectfont}% Bibliography support using natbib.sty

\theoremstyle{plain}% Theorem-like structures provided by amsthm.sty
\newtheorem{theorem}{Theorem}[section]
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{corollary}[theorem]{Corollary}
\newtheorem{proposition}[theorem]{Proposition}

\theoremstyle{definition}
\newtheorem{definition}[theorem]{Definition}
\newtheorem{example}[theorem]{Example}

\theoremstyle{remark}
\newtheorem{remark}{Remark}
\newtheorem{notation}{Notation}

% tightlist command for lists without linebreak
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}

% From pandoc table feature
\usepackage{longtable,booktabs,array}
\usepackage{calc} % for calculating minipage widths
% Correct order of tables after \paragraph or \subparagraph
\usepackage{etoolbox}
\makeatletter
\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
\makeatother
% Allow footnotes in longtable head/foot
\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
\makesavenoteenv{longtable}

\usepackage{float}
\usepackage{booktabs}
\usepackage{longtable}
\usepackage{threeparttable}
\floatplacement{figure}{H}
\floatplacement{table}{H}
\usepackage{caption}
\usepackage{hyperref}
\usepackage[utf8]{inputenc}
\def\tightlist{}
\usepackage{booktabs}
\usepackage{longtable}
\usepackage{array}
\usepackage{multirow}
\usepackage{wrapfig}
\usepackage{float}
\usepackage{colortbl}
\usepackage{pdflscape}
\usepackage{tabu}
\usepackage{threeparttable}
\usepackage{threeparttablex}
\usepackage[normalem]{ulem}
\usepackage{makecell}
\usepackage{xcolor}

\begin{document}

\articletype{}

\title{Divergent Impacts of COVID-19 School Closures on Youth Infection Dynamics: Evidence from 12 European Countries}

\author{\name{Author 1$^{1}$, Author 2$^{2}$}
\affil{$^{1}$Affiliation 1; $^{2}$Affiliation 2}
}

\maketitle

\begin{abstract}
The effectiveness of school closures as a COVID-19 control measure remains a subject of debate. This paper critically reassesses their impact by examining infection trends across various age groups in 12 European countries. We apply a dual analytical approach: Generalised Additive Models (GAMs) are used to capture complex, non-linear effects of closures on age-specific case numbers, while Transfer Entropy (TE) is employed to quantify directional transmission patterns between these age groups. Our findings reveal deviations from commonly held assumptions. While school closures were associated with a non-linear decline in overall national COVID-19 cases, the effects on children and young adults varied considerably. A consistent downward trend in infections was seen only in the pre-school age group. In contrast, school-aged children experienced a marked rise in COVID-19 cases following an initial period of stability or slight decrease after closures began. The Transfer Entropy analysis also identified asymmetric, directional patterns in transmission, revealing that infection trends in specific age groups could predict subsequent changes in others. These results challenge the assumption that school closures uniformly benefit younger populations and emphasise the need for age-specific analysis in pandemic planning and support the development of more nuanced, evidence-based public health policies.
\end{abstract}

\begin{keywords}
COVID-19; School Closures; Intergenerational Transmission; Non-linear effects; Infection dynamics.
\end{keywords}

\section{Introduction}\label{introduction}

@@

The GAM is fitted on the daily COVID-19 cases to test the hypothesis of a significant non-linear evolution of cases among age groups from 0 to 4, from 5 to 9, from 10 to 14, from 15 to 19, and from 20 to 24 \citep{wood2017generalized}. The model also estimates the overall non-linear effect by country, taking into account the interaction between age groups and countries as random intercepts and the interaction between time, countries, and the period of closure as random effects (Eq 1).

@@

\begin{align*}
  \tag{1}
  n\prime_t &\sim \text{Poisson}(\lambda_t) \\
  \log(\lambda_t) &= \beta_0 + \beta_1\,wave_t + \beta_2\,country_t + \beta_3\,age\,group_t \\
  &\quad + f_1(closure_t) + f_2(closure_t, country_t) \\
  &\quad + f_3(closure_t, age\,group_t) + f_4(stringency\,index_t) \\
  &\quad + f_5(government\,response\,index_t) + f_6(containment\,health\,index_t) \\
  &\quad + f_7(economic\,support\,index_t) +\epsilon_t
\end{align*}

@@

\begin{align}
  \tag{2}
  T_{ag\,x \rightarrow ag\,y}(k,l) = \sum_{ag\,x_{t+1}, ag\,x_t^{(k)}, ag\,y_t^{(l)}} 
  p\left(ag\,x_{t+1}, ag\,x_t^{(k)}, ag\,y_t^{(l)}\right) 
  \log \left(\frac{p\left(ag\,x_{t+1} \mid ag\,x_t^{(k)}, ag\,y_t^{(l)}\right)}{p\left(ag\,x_{t+1} \mid ag\,x_t^{(k)}\right)}\right)
\end{align}

\noindent where \(T_{ag\,x \rightarrow\,ag\,y}\) consequently measures the influence of the change dynamic from an age group \(X\) (or \(ag\,x\)) to another age group \(Y\) (or \(ag\,y\)) for every country (Eq 2).

@@

The data show that the trend of confirmed COVID-19 cases follows similar patterns across the selected European countries, with scales following the size of the population in these countries (Figure \ref{fig:overall}). Thus, the bigger the country, the higher the total number of COVID-19 cases.

\begin{figure}
\includegraphics[width=\textwidth]{manuscript_blind_files/figure-latex/overall-1} \caption{Cumulative COVID-19 cases number for selected European countries since the beginning of the pandemic. Source: COVerAGE-DB \citep{riffe2021data}.}\label{fig:overall}
\end{figure}

The evolution of COVID-19 cases reveals some similarities across all age groups. However, the influence of each wave on individual age groups also has some particularities (Figure \ref{fig:descriptive}). For example, the first wave was more important among the oldest age groups, whereas the third wave was more important among the youngest age groups.

\begin{figure}
\includegraphics[width=\textwidth]{manuscript_blind_files/figure-latex/descriptive-1} \caption{Periods of school closure since the beginning of the COVID-19 pandemic for selected European countries and their reason: regular academic break versus closure due to government decisions. Source: \citet{unesco2022https}.}\label{fig:descriptive}
\end{figure}

As outlined above, to evaluate the shape of the trend in the numbers of COVID-19 cases reported after the three school closures longer than 21 consecutive days, a GAM was fitted as described above, taking into account the overall effect across all the selected European countries, as well as the effect for age groups: 0 to 4, 5 to 9, 10 to 14, 15 to 19, and 20 to 24 years old. The obtained results satisfy the requirements to fit this model, which explains 80.2\% of the variation in COVID-19 cases.

Overall, the results revealed a decreasing non-linear effect of school closure at a country level for the selected European countries (Austria: \(\chi^2(5.82) = 3243.01\), \(p < 0.001\); Belgium: \(\chi^2(5.98) = 6206.45\), \(p < 0.001\); Bulgaria: \(\chi^2(5.89) = 258.19\), \(p < 0.001\); Croatia: \(\chi^2(5.1) = 740.24\), \(p < 0.001\); Estonia: \(\chi^2(5.93) = 1834.26\), \(p < 0.001\); France: \(\chi^2(1) = 2412.59\), \(p < 0.001\); Germany (\(\chi^2(5.98) = 3081.05\), \(p < 0.001\)); Greece: \(\chi^2(5.95) = 2423.67\), \(p < 0.001\); The Netherlands: \(\chi^2(4.97) = 5878.92\), \(p < 0.001\); Portugal: \(\chi^2(5.94) = 2692.56\), \(p < 0.001\); Slovakia (\(\chi^2(5.97) = 5335.74\), \(p < 0.001\); Spain: \(\chi^2(5.94) = 498.09\), \(p < 0.001\), see Figure \ref{fig:age}).

\begin{figure}
\includegraphics[width=\textwidth]{manuscript_blind_files/figure-latex/country-1} \caption{Standardized effect of the smooth term in Generalized Additive Model by country. Standardized effects are reported to compare the shape of the curve between countries.}\label{fig:country}
\end{figure}

\begin{figure}
\includegraphics[width=\textwidth]{manuscript_blind_files/figure-latex/age-1} \caption{Standardized effect of the smooth term in Generalized Additive Model by age group. Standardized effects are reported to compare the shape of the curve between age groups.}\label{fig:age}
\end{figure}

@@

\begin{figure}[H]
\includegraphics[width=\textwidth]{manuscript_blind_files/figure-latex/te-1} \caption{Matrix of Transfer Entropy coefficients according to every age group combination for each of the selected European country. Age groups on the x-axis are influencing the age groups on the y-axis (\(ag\,x \rightarrow\,ag\,y\)). The significance of each Transfer Entropy coefficient is provided in Appendix 2.}\label{fig:te}
\end{figure}

Considering all countries, the analysis of age groups reveals distinct patterns (Figure \ref{fig:te}). For the 0 to 4 age group, i.e., the pre-school group, there was a downward trend during the initial three weeks following school closure, followed by an increase during the fourth week (\(\chi^2(5.96) = 410.48\), \(p < 0.001\)). A similar, but more moderate, trend is observer for the age group ranging from 5 to 9 (\(\chi^2(5.95) = 878.29\), \(p < 0.001\)), where a decrease is observed during the first two weeks, followed by an increase. while the trend for the age group ranging from 10 to 14 is flat during the first two weeks, a similar increase is shown at the beginning of the third week of school closure (\(\chi^2(1) = 61.62\), \(p < 0.001\)). For age groups between 15 and 24, there is a notable surge immediately after school closure, followed by a decrease after 14 days (15 to 19 age group: \(\chi^2(5.97) = 7929.88\), \(p < 0.001\) and 20 to 24 age group: \(\chi^2(4.98) = 18386.65\), \(p < 0.001\)). Thus, while the total case number declined following school closures, among younger age groups only the pre-school age group had a consistent reduction in cases, while for other age groups, there was even an increase in cases following school closures.

@@

The results of the transfer entropy calculations between age groups for each of the 12 selected European countries are reported in Figure \ref{fig:te}. The absence of symmetry between influencing age groups (i.e., \(ag\,x\)) and influenced age groups (i.e., \(ag\,y\)) is found. Indeed, the change in COVID-19 cases in some age groups is influenced by other age groups, but they are not reciprocally influencing these age groups. Figure \ref{fig:te} shows how different age cohorts influence the COVID-19 case numbers of all age groups across countries. The upper left quadrant indicates how younger age cohorts are influencing older age cohorts, the bottom right quadrant indicates how older age cohorts are influencing younger age cohorts, finally, the lower left and upper right indicate how younger or older age cohorts are influencing themselves. By analyzing these quadrants, it is possible to identify similar patterns across multiple countries. Indeed, it appears that Austria, Germany, and The Netherlands have significantly higher \(T\) coefficients in the upper left quadrant of the matrix, which indicates that the daily changes in COVID-19 cases number in younger cohorts are predicting the daily changes in COVID-19 cases number in older cohorts. Alternatively, it appears that Austria, the Netherlands, Portugal, and Spain have significantly higher \(T\) coefficients in the lower right quadrant of the matrix, which indicates that the daily changes in COVID-19 cases number in older cohorts are predicting the daily changes in COVID-19 cases number in younger cohorts.

@@

The data can be accessed from the COVerAGE-DB OSF repository (\url{https://osf.io/mpwjq/}), from the Oxford Covid-19 Government Response Tracker (OxCGRT) ``covid-policy-dataset'' GitHub repository (\url{https://github.com/OxCGRT/covid-policy-dataset}), and from the UNESCO servers (\url{https://en.unesco.org/file/unesco-data-school-closures-february-2020-june-2022csv-zip}). All preprocessing, analyses and code used to build the submitted paper are available at \url{https://github.com/damien-dupre/covid_ts_causality}.

\bibliographystyle{tfcad}
\bibliography{bibliography.bib}

>>>>

\documentclass[Harvard,Times1COL]{WileyNJDv5}

\usepackage{natbib}
\bibliographystyle{wileyNJD-Harvard}

\hypersetup{
  colorlinks=true,
  linkcolor=blue,
  citecolor=blue,
  filecolor=black,
  urlcolor=black
}
\begin{document}

\articletype{Article Type: Research Article}

\received{Date Month Year}
\revised{Date Month Year}
\accepted{Date Month Year}
\journal{Journal of Policy Analysis and Management}
\volume{00}
\copyyear{2025}
\startpage{1}

% TODO: Inherited from WileyNJD example. Is this needed?
% \raggedbottom

\authormark{Dupré and Morgenroth}

\presentaddress{DCU Business School, Dublin 9, Ireland.}

% Include information for each author
  \author[1]{Damien Dupré}
  \author[1]{Edgar Morgenroth}

% Include information for each affiliation
\address[1]{%
  \orgdiv{%
    Business School%
    , %
    \orgname{%
      Dublin City University%
      , %
    }%
    \orgaddress{%
      \state{Dublin}%
      , %
      \country{Ireland}%
    }%
  }%
}

% Include information for each corresponder
      \corres{%
      %
        Damien Dupré%
      %
      \email{damien.dupre@dcu.ie}%
    }

\title{Divergent Impacts of COVID-19 School Closures on Youth Infection
Dynamics: Evidence from 12 European Countries}
\titlemark{COVID-19 School Closures and Youth Infection Dynamics}

\abstract[Abstract]{The effectiveness of school closures as a COVID-19
control measure remains a subject of debate. This paper critically
reassesses their impact by examining infection trends across various age
groups in 12 European countries. We apply a dual analytical approach:
Generalised Additive Models (GAMs) are used to capture complex,
non-linear effects of closures on age-specific case numbers, while
Transfer Entropy (TE) is employed to quantify directional transmission
patterns between these age groups. Our findings reveal deviations from
commonly held assumptions. While school closures were associated with a
non-linear decline in overall national COVID-19 cases, the effects on
children and young adults varied considerably. A consistent downward
trend in infections was seen only in the pre-school age group. In
contrast, school-aged children experienced a marked rise in COVID-19
cases following an initial period of stability or slight decrease after
closures began. The Transfer Entropy analysis also identified
asymmetric, directional patterns in transmission, revealing that
infection trends in specific age groups could predict subsequent changes
in others. These results challenge the assumption that school closures
uniformly benefit younger populations and emphasise the need for
age-specific analysis in pandemic planning and support the development
of more nuanced, evidence-based public health policies.}

{\keywords{COVID-19, School closures, Intergenerational
transmission, Non-linear effects, Infection dynamics.}

\maketitle
\section{Introduction}\label{introduction}

@@

The GAM is fitted on the daily COVID-19 cases to test the hypothesis of
a significant non-linear evolution of cases among age groups from 0 to
4, from 5 to 9, from 10 to 14, from 15 to 19, and from 20 to 24
\citep{wood2017generalized}. The model also estimates the overall
non-linear effect by country, taking into account the interaction
between age groups and countries as random intercepts and the
interaction between time, countries, and the period of closure as random
effects (Eq \ref{eq-gam}).

@@

\begin{equation}\phantomsection\label{eq-gam}{
\begin{aligned}[t]
  n\prime_t &\sim \text{Poisson}(\lambda_t) \\
  \log(\lambda_t) &= \beta_0 + \beta_1\,wave_t + \beta_2\,country_t + \beta_3\,age\,group_t \\
  &\quad + f_1(closure_t) + f_2(closure_t, country_t) \\
  &\quad + f_3(closure_t, age\,group_t) + f_4(stringency\,index_t) \\
  &\quad + f_5(government\,response\,index_t) + f_6(containment\,health\,index_t) \\
  &\quad + f_7(economic\,support\,index_t) +\epsilon_t
\end{aligned}
}\end{equation}

@@

\begin{equation}\phantomsection\label{eq-te}{
\begin{aligned}[t]
  T_{ag\,x \rightarrow ag\,y}(k,l) = \sum_{ag\,x_{t+1}, ag\,x_t^{(k)}, ag\,y_t^{(l)}} 
  p\left(ag\,x_{t+1}, ag\,x_t^{(k)}, ag\,y_t^{(l)}\right) 
  \log \left(\frac{p\left(ag\,x_{t+1} \mid ag\,x_t^{(k)}, ag\,y_t^{(l)}\right)}{p\left(ag\,x_{t+1} \mid ag\,x_t^{(k)}\right)}\right)
\end{aligned}
}\end{equation}

\noindent where \(T_{ag\,x \rightarrow\,ag\,y}\) consequently measures
the influence of the change dynamic from an age group \(X\) (or
\(ag\,x\)) to another age group \(Y\) (or \(ag\,y\)) for every country
(Eq \ref{eq-te}).

@@

The data show that the trend of confirmed COVID-19 cases follows similar
patterns across the selected European countries, with scales following
the size of the population in these countries
(Figure~\ref{fig-overall}). Thus, the bigger the country, the higher the
total number of COVID-19 cases.

\begin{figure}[h]

\centering{

\pandocbounded{\includegraphics[keepaspectratio]{manuscript_files/figure-pdf/fig-overall-1.png}}

}

\caption{\label{fig-overall}Cumulative COVID-19 cases number for
selected European countries since the beginning of the pandemic. Source:
COVerAGE-DB \citep{riffe2021data}.}

\end{figure}%

The evolution of COVID-19 cases reveals some similarities across all age
groups. However, the influence of each wave on individual age groups
also has some particularities (Figure~\ref{fig-descriptive}). For
example, the first wave was more important among the oldest age groups,
whereas the third wave was more important among the youngest age groups.

\begin{figure}[h]

\centering{

\pandocbounded{\includegraphics[keepaspectratio]{manuscript_files/figure-pdf/fig-descriptive-1.png}}

}

\caption{\label{fig-descriptive}Periods of school closure since the
beginning of the COVID-19 pandemic for selected European countries and
their reason: regular academic break versus closure due to government
decisions. Source: \citet{unesco2022https}.}

\end{figure}%

As outlined above, to evaluate the shape of the trend in the numbers of
COVID-19 cases reported after the three school closures longer than 21
consecutive days, a GAM was fitted as described above, taking into
account the overall effect across all the selected European countries,
as well as the effect for age groups: 0 to 4, 5 to 9, 10 to 14, 15 to
19, and 20 to 24 years old. The obtained results satisfy the
requirements to fit this model, which explains 80.2\% of the variation
in COVID-19 cases (Figure~\ref{fig-age}).

\begin{figure}[h]

\centering{

\pandocbounded{\includegraphics[keepaspectratio]{manuscript_files/figure-pdf/fig-age-1.png}}

}

\caption{\label{fig-age}Standardized effect of the smooth term in
Generalized Additive Model by age group. Standardized effects are
reported to compare the shape of the curve between age groups.}

\end{figure}%

Overall, the results revealed a decreasing non-linear effect of school
closure at a country level for the selected European countries (Austria:
\(\chi^2(5.82) = 3243.01\), \(p < 0.001\); Belgium:
\(\chi^2(5.98) = 6206.45\), \(p < 0.001\); Bulgaria:
\(\chi^2(5.89) = 258.19\), \(p < 0.001\); Croatia:
\(\chi^2(5.1) = 740.24\), \(p < 0.001\); Estonia:
\(\chi^2(5.93) = 1834.26\), \(p < 0.001\); France:
\(\chi^2(1) = 2412.59\), \(p < 0.001\); Germany
(\(\chi^2(5.98) = 3081.05\), \(p < 0.001\)); Greece:
\(\chi^2(5.95) = 2423.67\), \(p < 0.001\); The Netherlands:
\(\chi^2(4.97) = 5878.92\), \(p < 0.001\); Portugal:
\(\chi^2(5.94) = 2692.56\), \(p < 0.001\); Slovakia
(\(\chi^2(5.97) = 5335.74\), \(p < 0.001\); Spain:
\(\chi^2(5.94) = 498.09\), \(p < 0.001\), see Figure~\ref{fig-country}.

\begin{figure}[h]

\centering{

\pandocbounded{\includegraphics[keepaspectratio]{manuscript_files/figure-pdf/fig-country-1.png}}

}

\caption{\label{fig-country}Standardized effect of the smooth term in
Generalized Additive Model by country. Standardized effects are reported
to compare the shape of the curve between countries.}

\end{figure}%

@@

\begin{figure}[h]

\centering{

\pandocbounded{\includegraphics[keepaspectratio]{manuscript_files/figure-pdf/fig-te-1.png}}

}

\caption{\label{fig-te}Matrix of Transfer Entropy coefficients according
to every age group combination for each of the selected European
country. Age groups on the x-axis are influencing the age groups on the
y-axis (\(ag\,x \rightarrow\,ag\,y\)). The significance of each Transfer
Entropy coefficient is provided in Appendix 2.}

\end{figure}%

Considering all countries, the analysis of age groups reveals distinct
patterns (Figure~\ref{fig-te}). For the 0 to 4 age group, i.e., the
pre-school group, there was a downward trend during the initial three
weeks following school closure, followed by an increase during the
fourth week (\(\chi^2(5.96) = 410.48\), \(p < 0.001\)). A similar, but
more moderate, trend is observer for the age group ranging from 5 to 9
(\(\chi^2(5.95) = 878.29\), \(p < 0.001\)), where a decrease is observed
during the first two weeks, followed by an increase. while the trend for
the age group ranging from 10 to 14 is flat during the first two weeks,
a similar increase is shown at the beginning of the third week of school
closure (\(\chi^2(1) = 61.62\), \(p < 0.001\)). For age groups between
15 and 24, there is a notable surge immediately after school closure,
followed by a decrease after 14 days (15 to 19 age group:
\(\chi^2(5.97) = 7929.88\), \(p < 0.001\) and 20 to 24 age group:
\(\chi^2(4.98) = 18386.65\), \(p < 0.001\)). Thus, while the total case
number declined following school closures, among younger age groups only
the pre-school age group had a consistent reduction in cases, while for
other age groups, there was even an increase in cases following school
closures.

@@

The results of the transfer entropy calculations between age groups for
each of the 12 selected European countries are reported in
Figure~\ref{fig-te}. The absence of symmetry between influencing age
groups (i.e., \(ag\,x\)) and influenced age groups (i.e., \(ag\,y\)) is
found. Indeed, the change in COVID-19 cases in some age groups is
influenced by other age groups, but they are not reciprocally
influencing these age groups. F@fig-te shows how different age cohorts
influence the COVID-19 case numbers of all age groups across countries.
The upper left quadrant indicates how younger age cohorts are
influencing older age cohorts, the bottom right quadrant indicates how
older age cohorts are influencing younger age cohorts, finally, the
lower left and upper right indicate how younger or older age cohorts are
influencing themselves. By analyzing these quadrants, it is possible to
identify similar patterns across multiple countries. Indeed, it appears
that Austria, Germany, and The Netherlands have significantly higher
\(T\) coefficients in the upper left quadrant of the matrix, which
indicates that the daily changes in COVID-19 cases number in younger
cohorts are predicting the daily changes in COVID-19 cases number in
older cohorts. Alternatively, it appears that Austria, the Netherlands,
Portugal, and Spain have significantly higher \(T\) coefficients in the
lower right quadrant of the matrix, which indicates that the daily
changes in COVID-19 cases number in older cohorts are predicting the
daily changes in COVID-19 cases number in younger cohorts.

@@

The data can be accessed from the COVerAGE-DB OSF repository
(https://osf.io/mpwjq/), from the Oxford Covid-19 Government Response
Tracker (OxCGRT) ``covid-policy-dataset'' GitHub repository
(https://github.com/OxCGRT/covid-policy-dataset), and from the UNESCO
servers
(https://en.unesco.org/file/unesco-data-school-closures-february-2020-june-2022csv-zip).
All preprocessing, analyses and code used to build the submitted paper
are available at https://github.com/damien-dupre/covid\_ts\_causality.

\section{References}\label{references}

\renewcommand{\bibsection}{}
\bibliography{bibliography.bib}

### 2025-06-05 manuscript_tf/manuscript_blind.tex
update
update + njd

\author{\name{Damien Dupré$^{1}$, Edgar Morgenroth$^{1}$}
\affil{$^{1}$Dublin City University Business School, Glasnevin, Dublin 9, Ireland}
}

@@

The data can be accessed from the COVerAGE-DB OSF repository (\url{https://osf.io/mpwjq/}), from the Oxford Covid-19 Government Response Tracker (OxCGRT) ``covid-policy-dataset'' GitHub repository (\url{https://github.com/OxCGRT/covid-policy-dataset}), and from the UNESCO servers (\url{https://en.unesco.org/file/unesco-data-school-closures-february-2020-june-2022csv-zip}). All preprocessing, analyses and code used to build the submitted paper are available at \url{https://github.com/damien-dupre/covid_ts_causality}.

>>>>

\author{\name{Author 1$^{1}$, Author 2$^{2}$}
\affil{$^{1}$Affiliation 1; $^{2}$Affiliation 2}
}

@@

The data can be accessed from the COVerAGE-DB OSF repository (\url{https://osf.io/mpwjq/}), from the Oxford Covid-19 Government Response Tracker (OxCGRT) ``covid-policy-dataset'' GitHub repository (\url{https://github.com/OxCGRT/covid-policy-dataset}), and from the UNESCO servers (\url{https://en.unesco.org/file/unesco-data-school-closures-february-2020-june-2022csv-zip}). All preprocessing, analyses and code used to build the submitted paper are available at {[}link hidden for blind peer-review process{]}.
